\addcontentsline{toc}{section}{References}
\begin{thebibliography}{15}
    \scriptsize
    \bibitem[Bartolinis, 1982]{bartolinis} W. Bartolini and P. Bartolini, “Experimental studies of the acoustics of classic and flamenco guitars,” J. Guitar Acoustics 6, 74-103 (1982)

    \bibitem[Byers, 1996]{byers} Byers, Greg. “Classic guitar intonation,” Am. Lutherie 47, 1-11 (1996), \url{http://www.laguitarra-blog.com/wp-content/uploads/2012/01/luthieria-classical-guitar-intonation-greg-byers.pdf}
    
    \bibitem[Varieschi, 2010]{varieschi} Varieschi, Gabriele U., and Christina M. Gower. “Intonation and Compensation of Fretted String Instruments.” American Journal of Physics, vol. 78, no. 1, American Institute of Physics, Jan. 2010, pp. 47–55, \url{https://doi.org/10.1119/1.3226563}.

    \bibitem[Steinhaus, 1999]{mersenne} Steinhaus, Hugo (1999). Mathematical Snapshots 3rd ed. New York: Dover, p. 301, 1999.
    
    \bibitem[Nov]{yuval} Nov, Yuval. "Explaining the Equal Temperament", \url{https://www.yuvalnov.org/temperament/}.

    \bibitem[Mottola]{eqn6} Mottola, R. M. “Liutaio Mottola Lutherie Information Website.” Liutaio Mottola Lutherie Information Website, \url{https://www.liutaiomottola.com/formulae/fret.htm}.

    \bibitem[Špakula, 2011]{spakula} Špakula, Ján. "Topic 11 Binomial Theorem | Lecture Notes - Maths A - Foundation Year." 7 Dec. 2021, \url{https://www.personal.soton.ac.uk/js2m12/fyA/binomial-theorem.html}.

    \bibitem[Nemeroff, 2023]{scale} Nemeroff, Ben. "Stratocaster Buying Guide: Fender Insiders Compare 8 Electric Guitar Models." 8 Mar. 2023, \url{https://www.fender.com/articles/instruments/fender-stratocaster-buying-guide-7-strat-models-compared}.

    \bibitem[Suits, 1998]{freq_chart} Suits, Bryan (1998). "Frequencies of Musical Notes, A4 = 440 Hz". Physics of Music — Notes. Michigan Tech University, \url{https://pages.mtu.edu/~suits/notefreqs}.
    
    \bibitem[Polak et al., 2018]{polak} Polak, Robert D., et al. “Determining Young’s Modulus by Measuring Guitar String Frequency.” The Physics Teacher, American Association of Physics Teachers, Jan. 2018, \url{https://doi.org/10.1119/1.5021447}.

    \bibitem[ASTM A228 Steel (UNS K08500)]{astm} ASTM A228 Steel (UNS K08500), \url{https://www.matweb.com/search/datasheet_print.aspx?matguid=4bcaab41d4eb43b3824d9de31c2c6849}.

    \bibitem[StewMac.com]{stewmac} StewMac, “String Action Gauge Instructions.” \url{https://www.stewmac.com/video-and-ideas/online-resources/neck-building-and-repair-and-setup/string-action-gauge-instructions}.

    \bibitem[VA2020 Website]{va20} \url{https://www.sillanumsoft.org/}.

    \bibitem[Suits, 1998]{cents} Suits, Bryan (1998). "Making Sense of Cents". Physics of Music — Notes. Michigan Tech University, \url{https://pages.mtu.edu/~suits/cents}.

    \bibitem[Loeffler, 2006]{loeffler} Loeffler, D.B. (April 2006). Instrument Timbres and Pitch Estimation in Polyphonic Music (Master's). Department of Electrical and Computer Engineering, Georgia Tech. \url{https://web.archive.org/web/20071218232401/http://etd.gatech.edu/theses/available/etd-04102006-142310/}

    \bibitem[Lane]{lane} Lane, David M. "Standard Error of the Estimate.", Online Stat Book, \url{https://www.onlinestatbook.com/2/regression/accuracy.html.}

\end{thebibliography}